Predicting I/O-performance in HPC using Artificial Neural Networks

### 2016-03-18 Poster/main.tex
Tabelle um rspe erweitert, erste version des Abstracts

@@

\title{Predicting I/O performance in HPC using Artificial Neural Networks} % Poster title

@@

	\begin{table}
		\vspace{0ex}
		\begin{tabular}{l|r|r}%
			&  \multicolumn{2}{|c}{mean absolut error (s)}\\ \hline
			%\toprule
			Modell & seq. access & rnd. access\\ \hline
			%\midrule
			Linear regression & $7.6\cdot 10^-5$ & $4.76\cdot 10^-3$ \\
			ANN & $6.0\cdot 10^-5$ & $3.13\cdot 10^-3$ \\
			ANN + time dependencies & $5.7\cdot 10^-5$ & $3.05\cdot 10^-3$\\
			ANN + error classes & $2.0\cdot 10^-5$ & $1.03\cdot 10^-3$ \\
			%\bottomrule
		\end{tabular}
		\caption{Mean absolut errors of the different models for the two different file access patterns used in the benchmark-tests.}
		\label{residues}
	\end{table}

@@

	\setbeamercolor{block alerted title}{fg=black,bg=white} % Change the alert block title colors
	\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
	\vspace*{-2cm}
	\begin{exampleblock}{}
		\vspace*{-1.2cm}
		%\hspace*{5cm}
		\textbf{Contact Information:}
		\vspace*{-0.4cm}
		\begin{itemize}
			%\item Web: \href{http://wr.informatik.uni-hamburg.de}{http://wr.informatik.uni-hamburg.de}
			\item \href{mailto:2schmid@informatik.uni-hamburg.de}{2schmid@informatik.uni-hamburg.de}
			%\item \href{mailto:juliankunkel@googlemail.com}{juliankunkel@googlemail.com}
		\end{itemize}

>>>>

%\setbeamercolor{bibliography entry author}{fg=red}
%\setbeamercolor{bibliography entry title}{fg=blue} 
\setbeamercolor{bibliography entry location}{fg=DarkGray} 
%\setbeamercolor{bibliography entry note}{fg=cyan}

@@

\title{Predicting I/O-performance in HPC using Artificial Neural Networks} % Poster title

@@

	\begin{table}
		\scriptsize
		\vspace{0.4cm}
		\begin{tabular}{l|r|r|r|r}%
			&  \multicolumn{2}{|c}{MAE (s)}&  \multicolumn{2}{|c}{MSPE (\%)}\\ \hline
			%\toprule
			Modell & seq. access & rnd. access & seq. access & rnd. access\\ \hline
			%\midrule
			Linear regression & $7.6\cdot 10^-5$ & $4.76\cdot 10^-3$ & 59 & 14185  \\
			ANN & $6.0\cdot 10^-5$ & $3.13\cdot 10^-3$ & 22 & 530 \\
			ANN + time dependencies & $5.7\cdot 10^-5$ & $3.05\cdot 10^-3$ & 22 & 619\\
			ANN + error classes & $2.0\cdot 10^-5$ & $1.03\cdot 10^-3$ & 14 & 119\\
			%\bottomrule
		\end{tabular}
		\caption{Mean absolut errors and mean square percentage errors of the different models for the two different file access patterns used in the benchmark-tests.}
		\label{residues}
	\end{table}

@@

	\setbeamercolor{block alerted title}{fg=black,bg=white} % Change the alert block title colors
	\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
	\vspace*{-2cm}
	\begin{exampleblock}{}
		\vspace*{-1cm}
		%\hspace*{5cm}
		\textbf{Contact Information:}
		\vspace*{-0.4cm}
		\begin{itemize}
			%\item Web: \href{http://wr.informatik.uni-hamburg.de}{http://wr.informatik.uni-hamburg.de}
			\item \href{mailto:2schmid@informatik.uni-hamburg.de}{2schmid@informatik.uni-hamburg.de}
			%\item \href{mailto:juliankunkel@googlemail.com}{juliankunkel@googlemail.com}
		\end{itemize}
